---
title: "RWorksheet#5_Group6"
author: "Bagilidad, Calopez, De Guzman, Talon"
date: "2023-11-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.


```{r}
install.packages("rvest")
install.packages("dplyr")
install.packages("polite")
install.packages("tidyverse")

library(rvest)
library(dplyr)
library(polite)
library(tidyverse)

url<- "https://www.imdb.com/chart/tvmeter/"
 
session <- bow(url, user_agent = "For Educational Purposes")

imdb <- read_html(url)

#ranks
ranks <- scrape(session) %>%
html_nodes("div.sc-94da5b1b-0") %>%
  html_text
ranks
cleaned_ranks <- substr(ranks,1,2)

ranks50<- cleaned_ranks[1:50]
ranks50

#titles
titles <- scrape(session) %>%
  html_nodes("h3.ipc-title__text") %>%
  html_text
titles
titles50 <- titles[2:51]
titles50

#ratings
ratings <- scrape(session) %>%
html_nodes("span.ipc-rating-star.ipc-rating-star--base.ipc-rating-star--imdb.ratingGroup--imdb-rating") %>%
  html_text

cleaned_ratings <- substr(ratings,1,3)
cleaned_ratings
ratings50 <- cleaned_ratings[1:50]
ratings50


#peoples vote
people_vote <- scrape(session)%>%
  html_nodes("span.ipc-rating-star--voteCount")%>%
  html_text()

people_vote50 <- people_vote[1:50]
people_vote50

cleaned_vote <- gsub("\\(|\\)", "", people_vote50)
cleaned_vote

#episodes

episodes <- scrape(session)%>%
  html_nodes("span.sc-43986a27-8:nth-of-type(2)") %>%
  html_text()
episodes50 <- episodes[1:50]
episodes50


#year
year <- scrape(session)%>%
  html_nodes("span.sc-43986a27-8:nth-of-type(1)") %>%
  html_text()
year50 <- year[1:50]
year50

#dataframe
topTv_df <- data.frame(Titles = titles50,
                       Ranks = ranks50,
                       Ratings = ratings50,
                       People_Votes = cleaned_vote,
                       Episodes = episodes50,
                       Year = year50
                       )
topTv_df


```

2. From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the
reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.

```{r}

#First tv show: Breaking Bad

BreakingBad_Link <- "https://www.imdb.com/title/tt0903747/reviews?ref_=tt_urv"
session2 <- bow(BreakingBad_Link, user_agent = "Educational Purposes")
session2

#Reviewers data for Breaking Bad
BreakingBad_Title <- scrape(session2)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
BreakingBad_Title

BreakingBad_RevName <- scrape(session2)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
BreakingBad_RevName

BreakingBad_RevDate <- scrape(session2) %>%
  html_nodes("span.review-date") %>%
  html_text()
BreakingBad_RevDate

BreakingBad_UserRating <- scrape(session2) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
BreakingBad_UserRating

BreakingBad_TitleRev <- scrape(session2) %>%
  html_nodes(" a.title") %>%
  html_text()
BreakingBad_TitleRev2 <- gsub("\n ","", BreakingBad_TitleRev)
BreakingBad_TitleRev2

BreakingBad_TextRev <- scrape(session2) %>%
  html_nodes("div.text") %>%
  html_text()
BreakingBad_TextRev

BreakingBad_Df <- data.frame(Tv_Shows = BreakingBad_Title,
                             Reviewer_Name = BreakingBad_RevName,
                             Reviewer_Date = BreakingBad_RevDate,
                             Reviewer_Rating = BreakingBad_UserRating,
                             Title_Review = BreakingBad_TitleRev2,
                             Text_Review = BreakingBad_TextRev)
BreakingBad_Df




#Second TV Show: The Boys

TheBoys_Link <- "https://www.imdb.com/title/tt1190634/reviews/?ref_=tt_ql_2"
session3 <- bow(TheBoys_Link, user_agent = "Educational Purposes")
session3

#Reviewers data for The Boys
TheBoys_Title <- scrape(session3)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
TheBoys_Title

TheBoys_RevName <- scrape(session3)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
TheBoys_RevName

TheBoys_RevDate <- scrape(session3) %>%
  html_nodes("span.review-date") %>%
  html_text()
TheBoys_RevDate

TheBoys_UserRating <- scrape(session3) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
TheBoys_UserRating


TheBoys_TitleRev <- scrape(session3) %>%
  html_nodes(" a.title") %>%
  html_text() %>% str_trim()
TheBoys_TitleRev


TheBoys_TextRev <- scrape(session3) %>%
  html_nodes("div.text") %>%
  html_text()
TheBoys_TextRev

TheBoys_Df <- data.frame(Tv_Shows = TheBoys_Title,
                         Reviewer_Name = TheBoys_RevName[1:15],
                         Reviewer_Date = TheBoys_RevDate[1:15],
                         Reviewer_Rating = TheBoys_UserRating[1:15],
                         Title_Review = TheBoys_TitleRev[1:15],
                         Text_Review = TheBoys_TextRev[1:15])
TheBoys_Df

#Third TV Show: Game of Thrones

GameofThrones_Link <- "https://www.imdb.com/title/tt0944947/reviews/?ref_=tt_ql_2"
session4 <- bow(GameofThrones_Link, user_agent = "Educational Purposes")
session4

#Reviewers data for Game of Thrones
GameofThrones_Title <- scrape(session4)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
GameofThrones_Title



GameofThrones_RevName <- scrape(session4)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
GameofThrones_RevName

GameofThrones_RevDate <- scrape(session4) %>%
  html_nodes("span.review-date") %>%
  html_text()
GameofThrones_RevDate

GameofThrones_UserRating <- scrape(session4) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
GameofThrones_UserRating


GameofThrones_TitleRev <- scrape(session4) %>%
  html_nodes(" a.title") %>%
  html_text() %>% str_trim()
GameofThrones_TitleRev


GameofThrones_TextRev <- scrape(session4) %>%
  html_nodes("div.text") %>%
  html_text()
GameofThrones_TextRev

GameofThrones_Df <- data.frame( Tv_Shows = GameofThrones_Title,
                                Reviewer_Name = GameofThrones_RevName[1:15],
                                Reviewer_Date = GameofThrones_RevDate[1:15],
                                Reviewer_Rating = GameofThrones_UserRating[1:15],
                                Title_Review = GameofThrones_TitleRev[1:15],
                                Text_Review = GameofThrones_TextRev[1:15])
GameofThrones_Df


#Fourth TV Show: Rick and Morty

RickMorty_Link <- "https://www.imdb.com/title/tt2861424/reviews/?ref_=tt_ql_2"
session5 <- bow(RickMorty_Link, user_agent = "Educational Purposes")
session5

#Reviewers data for Rick and Morty
RickMorty_Title <- scrape(session5)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
RickMorty_Title

RickMorty_RevName <- scrape(session5)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
RickMorty_RevName

RickMorty_RevDate <- scrape(session5) %>%
  html_nodes("span.review-date") %>%
  html_text()
RickMorty_RevDate

RickMorty_UserRating <- scrape(session5) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
RickMorty_UserRating


RickMorty_TitleRev <- scrape(session5) %>%
  html_nodes(" a.title") %>%
  html_text() %>% str_trim()
RickMorty_TitleRev


RickMorty_TextRev <- scrape(session5) %>%
  html_nodes("div.text") %>%
  html_text()
RickMorty_TextRev

RickMorty_Df <- data.frame(  Tv_Shows = RickMorty_Title,
                             Reviewer_Name = RickMorty_RevName[1:15],
                             Reviewer_Date = RickMorty_RevDate[1:15],
                             Reviewer_Rating = RickMorty_UserRating[1:15],
                             Title_Review = RickMorty_TitleRev[1:15],
                             Text_Review = RickMorty_TextRev[1:15])
RickMorty_Df


#Fifth TV Show: The Office

TheOffice_Link <- "https://www.imdb.com/title/tt0386676/reviews/?ref_=tt_ql_2"
session6 <- bow(TheOffice_Link, user_agent = "Educational Purposes")
session6

#Reviewers data for The Office

TheOffice_Title <- scrape(session6)%>%
  html_nodes("a[itemprop='url']") %>%
  html_text()
TheOffice_Title

TheOffice_RevName <- scrape(session6)%>%
  html_nodes(".display-name-link a") %>%
  html_text()
TheOffice_RevName

TheOffice_RevDate <- scrape(session6) %>%
  html_nodes("span.review-date") %>%
  html_text()
TheOffice_RevDate

TheOffice_UserRating <- scrape(session6) %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text() %>% str_trim()
TheOffice_UserRating


TheOffice_TitleRev <- scrape(session6) %>%
  html_nodes(" a.title") %>%
  html_text() %>% str_trim()
TheOffice_TitleRev


TheOffice_TextRev <- scrape(session6) %>%
  html_nodes("div.text") %>%
  html_text()
TheOffice_TextRev

TheOffice_Df <- data.frame(  Tv_Show = TheOffice_Title,
                             Reviewer_Name = TheOffice_RevName[1:15],
                             Reviewer_Date = TheOffice_RevDate[1:15],
                             Reviewer_Rating = TheOffice_UserRating[1:15],
                             Title_Review = TheOffice_TitleRev[1:15],
                             Text_Review = TheOffice_TextRev[1:15])
TheOffice_Df


TvShows_Bind <- rbind(BreakingBad_Df,TheBoys_Df,GameofThrones_Df,RickMorty_Df,TheBoys_Df)
TvShows_Bind

```
3. Create a time series graph for the tv shows released by year. Which year has the most number of tv
shows released?

```{r}
library(ggplot2)
library(dplyr)

ggplot(topTv_df, aes(x = Year, fill = Year)) +
  geom_bar() +
  labs(title = "Number of TV Shows Released by Year",
       x = "Year",
       y = "Number of TV Shows") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
axis.text.x = element_text(angle = 44, hjust = 1))



cat("The year with the most number of tv shows is", topTv_df$Year[1])
```

4. Select 3 products from Amazon of the same category. Extract the price, description, ratings and
reviews of each product.
install.packages("rvest")
install.packages("dplyr")
install.packages("polite")
install.packages("tidyverse")
```{r}
# FIRST ITEM
library(rvest)
library(dplyr)
library(polite)
library(tidyverse)

item1 <- "https://www.amazon.com/SteelSeries-Worlds-Fastest-Mechanical-Keyboard/dp/B0BF64DN6H/ref=sr_1_10?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&keywords=gaming%2Bkeyboard&pd_rd_r=0f6ba081-7c35-4aa4-bc81-6422dc3dfb37&pd_rd_w=qsoSW&pd_rd_wg=5V8Nr&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=6GPK37Q4SVBEWJXAB6A4&qid=1702295919&sr=8-10&th=1"
session1 <- html_session(item1, user_agent = "Educational Purposes")

price1 <- session1 %>%
  html_nodes('span.a-offscreen')%>%
  html_text()%>%
  trimws()
price1

description1 <- session1 %>%
  html_nodes('.a-unordered-list .a-list-item') %>%
  html_text() %>%
  trimws()
description1

prodrating1 <- session1 %>%
  html_nodes('.a-icon-star .a-icon-alt') %>%
  html_text() %>%
  trimws()
prodrating1

prodreview1 <- session1 %>%
  html_nodes('#acrCustomerReviewText') %>%
  html_text() %>%
  trimws()
prodreview1

# SECOND ITEM
item2 <- "https://www.amazon.com/MageGee-Keyboard-Waterproof-Backlit-Computer/dp/B08NSXRQ98/ref=sr_1_9?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&keywords=gaming%2Bkeyboard&pd_rd_r=0f6ba081-7c35-4aa4-bc81-6422dc3dfb37&pd_rd_w=qsoSW&pd_rd_wg=5V8Nr&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=6GPK37Q4SVBEWJXAB6A4&qid=1702295919&sr=8-9&th=1"
session2 <- html_session(item2, user_agent = "Educational Purposes")

price2 <- session1 %>%
  html_nodes('.a-offscreen')%>%
  html_text()%>%
  trimws()
price2

description2 <- session2 %>%
  html_nodes('.a-unordered-list .a-list-item') %>%
  html_text() %>%
  trimws()
description2

prodrating2 <- session2 %>%
  html_nodes('.a-icon-star .a-icon-alt') %>%
  html_text() %>%
  trimws()
prodrating2

prodreview2 <- session2 %>%
  html_nodes('#acrCustomerReviewText') %>%
  html_text() %>%
  trimws()
prodreview2

# THIRD ITEM
item3 <- "https://www.amazon.com/RK-ROYAL-KLUDGE-Mechanical-Ultra-Compact/dp/B089GN2KBT/ref=sr_1_8?_encoding=UTF8&content-id=amzn1.sym.12129333-2117-4490-9c17-6d31baf0582a&keywords=gaming%2Bkeyboard&pd_rd_r=0f6ba081-7c35-4aa4-bc81-6422dc3dfb37&pd_rd_w=qsoSW&pd_rd_wg=5V8Nr&pf_rd_p=12129333-2117-4490-9c17-6d31baf0582a&pf_rd_r=6GPK37Q4SVBEWJXAB6A4&qid=1702295919&sr=8-8&th=1"
session3 <- html_session(item3, user_agent = "Educational Purposes")

price3 <- session3 %>%
  html_nodes('#priceblock_ourprice') %>%
  html_text() %>%
  trimws()
price3

description3 <- session3 %>%
  html_nodes('.a-unordered-list .a-list-item') %>%
  html_text() %>%
  trimws()
description3

prodrating3 <- session3 %>%
  html_nodes('.a-icon-star .a-icon-alt') %>%
  html_text() %>%
  trimws()
prodrating3

prodreview3 <- session3 %>%
  html_nodes('#acrCustomerReviewText') %>%
  html_text() %>%
  trimws()
prodreview3

```

